### 2015-06-28 narrative/intro.tex
Significant edits to guide the understanding of the rest of the proposal in the beginning of the introduction. Key idea: user and storage system cooperating on storage goals.

Exascale scientific discovery will be severely bottlenecked without
sufficient new research into managing and storing the large amounts of data
that will be produced during the simulation, and analyzed for months
afterwards.
%
In this project we will demonstrate novel techniques to facilitate efficient
mapping of data objects, even partitioning individual variables, from the
user space onto multiple storage tiers, and enable application-guided data
reductions/transformations to address capacity and bandwidth bottlenecks,
while constraining the error to be within user provided bounds.
%
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes, and expedite insights into critical
scientific processes, demonstrating the validity of our approach in key DOE
domains. Our techniques will be to research novel techniques into a Scalable
Storage Software Infrastructure by integrating services from the middle-ware
layer which will talk to the applications, with the Storage system. The
negotation between these layers will be a fundamental service which we will
create in this project to ensure that users will be able to save `'the
best'' amount of data in the different storage tiers.

@@

To address these challenges we will We are proposing to combine the applications
knowledge from ORNL, from the ADIOS project, with the SNL LWFS system and storage system knowledge, the
metadata and storage systems knowledge of UCSC, and the middleware expertise of
Rutgers to investigate how to make a data, workflow, and application aware
storage system.

@@

In this project we extend ADIOS with new APIs and novel techniques to talk to the
storage back-end. We will also test our ideas on the next generation OLCF system along with
the next generation NERSC system. One of the clear challenges of this work will be in accessing new APIs which
will give the applications much more control and flexibility of their I/O.
%
In this project we will make use of the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project, where Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, are added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project demonstrated that using a core
object storage system with integrated security providing authentication and
authorization services, customized storage interfaces could be developed with
exactly the overhead required for different applications. The second phase of
LWFS, known as Sirocco~\cite{sirocco}, is investigating how to manage storage
devices for efficient and scalable storage performance.  Sirocco has been in
process for three years and has a usable storage infrastructure system.

@@

\subsection{Writing Perspective}
\label{subsec:sim-perspective}
From the perspective of the simulation scientist, they want to be able to
have knowledge about how much time they will put into writing their data,
and how much storage space they will be able to get during the lifetime of
their simulations. Furthermore, they would like the ability to get a certain
amount of Quality of Service such that they can then make decisions when the
expected bandwidth, for example is less than what they desire. The user will
then place in a certain set of rules which the system can make autonomic
decisions to help decide what should be done.
%

@@

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it needs to manage the data from
a given user request amongst all of the request and try to optimize the
entire system. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By maiming a certain level of quality
of service the system must potentially lock out users with lower currency
they want to place in the reading or writing of their data. The storage
system must also automatically move data from one tier of the storage to
another, without effecting the quality of service that it guarantees at the
time of questioning. The storage system must also look at ways to organize
data amongst all of the tiers of storage in one consistent way.

One of the clear research objectives of this project is to understand how the storage system can interact
with the middleware (application-aware) piece so that the data with the highest utility is kept on the fastest 
layers of the storage system for as long as specified. Clearly we need to maintain some sort of QoS such that
we can give fuzzy-estimates of the time it will take to write/read data from the different layers, and clearly it is critical
that the storage system can manage the data across all of the layers. We will use learning techniques to automatically
migrate data sub-objects across the hierarchy as well as to eventually evict data which is large and has very low utility.

\subsection{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of the users who want to read in the data from their
simulations, and then operate on this data and possibly write data, we see
that in general these users will be running on much less compute resources
than the users who are running the simulation. One of the important aspects
of this class of user is that they want a reduction of latency and they
require a certain amount of quality of service as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it terms into 1,000s, the user typically tends to either wait
another day for doing their analysis, or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data.

>>>>

Exascale scientific discovery will be severely bottlenecked without
sufficient new research into managing and storing the large amounts of data
that will be produced during the simulation, and analyzed for months
afterwards.
%
In this project we will demonstrate a cooperative approach for storing data
where the user and the storage system work together to achieve the best data
quality and performance based on data features, storage tier characteristics,
and system state. We will investigate novel techniques to facilitate efficient
mapping of data objects, even partitioning individual variables, from the user
space onto multiple storage tiers and enable application-guided data
reductions/transformations to address capacity and bandwidth bottlenecks while
constraining the error to be within user provided bounds.
%
We will address the associated I/O and storage challenges in the context of
current and emerging storage landscapes and expedite insights into critical
scientific processes demonstrating the validity of our approach in key DOE
domains. We will research novel techniques into a Scalable
Storage Software Infrastructure integrating services from the middle-ware
layer adapted to each application with Storage System features to support the
novel data distribution both horizontally and vertically across the storage
system. The negotation between these layers will be a fundamental service 
to ensure that users will be able to save `'the best'' amount of data using the
right storage technology available at request time across the entire storage
stack.

@@

To address these challenges we will We are proposing to combine the
applications knowledge from ORNL, from the ADIOS project, with the SNL
Lightweight File Systems project and storage system knowledge, the metadata
management and storage systems knowledge of UCSC, and the middleware expertise
of Rutgers to investigate how to make a data, workflow, and application aware
storage system.

@@

In this project we extend ADIOS~\cite{adios} with new APIs and novel techniques
to talk to the storage back-end. The key idea is offering the ability to
negotiate with the storage system to agree on the tradeoff between data quality
and response time.  We will test our ideas on the next generation OLCF,
SNL/LANL, and  NERSC systems.
%
In this project we will make use of the many inovations we discovered in 
the Lightweight File Systems~\cite{lwfs} (LWFS) project, where Sandia sought to
demonstrate stripping down a file system to the bare minimum features required
for any storage system. Then, additional functionality and semantics, such as
POSIX-style directories and consistency requirements, are added in using
auxiliary services separate from the stack or by layering providing a new
interface to the storage system. The project's first phase demonstrated that
using a core object storage system with integrated security providing
authentication and authorization services, customized storage interfaces could
be developed with exactly the overhead required for different applications. The
second phase of LWFS, known as Sirocco~\cite{sirocco}, is investigating how to
manage storage devices for efficient and scalable storage performance.  Sirocco
has been in process for three years and has a usable storage infrastructure
system.

@@

\subsection{Writing Perspective}
\label{subsec:sim-perspective}
From the perspective of the simulation scientist, they want to be able to
have knowledge about how much time they will put into writing their data,
and how much storage space they will be able to get during the lifetime of
their simulations. Furthermore, they would like the ability to get a certain
amount of Quality of Service such that they can then make decisions when the
expected bandwidth, for example, is less than what they desire. The user will
then place in a certain set of rules which the system can make autonomic
decisions to help decide what should be done.
%

@@

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it needs to manage the data from
a given user request amongst all of the request and try to optimize the
entire system. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the system must potentially lock out users with lower currency
they want to place in the reading or writing of their data. The storage
system must also automatically move data from one tier of the storage to
another, without effecting the quality of service that it guarantees at the
time of questioning. The storage system must also look at ways to organize
data amongst all of the tiers of storage in one consistent way.

One of the clear research objectives of this project is to understand how the
storage system can interact with the middleware (application-aware) piece so
that the data with the highest utility is kept on the fastest layers of the
storage system for as long as specified. Clearly we need to maintain 
QoS such that fuzzy-estimates of the time it will take to write/read data from
the different layers informs any migration/eviction decisions, and clearly it
is critical that the storage system can manage the data across all of the
layers. We will use learning techniques to automatically migrate data
sub-objects across the hierarchy as well as to eventually evict data which is
large and has very low utility.

\subsection{Reading  Perspective}
\label{subsec:reading-perspective}
From the perspective of the users who want to read in the data from their
simulations, and then operate on this data and possibly write data, we see
that in general these users will be running on much less compute resources
than the users who are running the simulation. One of the important aspects
of this class of user is that they want a reduction of latency and they
require a certain amount of quality of service as well. When someone is
doing interactive analysis and expects that the data they read in is about
10s, but it turns into 1,000s, the user typically tends to either wait
another day for doing their analysis or gets frustrated and reads much less
data than they really need to. Furthermore the user tends to read in just a
small sample of the data without much knowledge if they are missing
important pieces of the data.
